ManuscriptGAM

### 2024-03-13 Code/Plots_GAM.Rmd
Generated .tiff for GAMs

#"..", takes up a level in the directory path
DataIn <- file.path("..","Data", "CleanData")
DataOut <- file.path("..","Data", "CleanData")
PlotsPath <- file.path("..","Output", "Figures")

@@

# comment rows that are not included in grid arrange 
LayoutNiche <- rbind(
                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(1, 1, 1, 1, 4),   # For 250 uM O2
                     c(1, 1, 1, 1, 4)    # For 250 uM O2
                     )

@@

p3_Red <- grid.arrange(
                       ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                          theme(legend.position = 'none'), 
                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                         theme(legend.position = 'none'), 
                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                         theme(legend.position = 'none'), 
                        legend1, 
                        legend2, 
                        legend3, 
                       layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )

# for presentation
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)

@@

p3_Blue <- grid.arrange(
                         ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                           theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                        ContourIntO2 +  labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                        ContourHighO2 + labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                         legend1, 
                        legend2, 
                        legend3, 
                        layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 10, width = 6)

# for presentation
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 7.6, width = 6)

@@

```{r save png}
 ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
```

>>>>

#"..", takes up a level in the directory path
DataIn <- file.path("..","Data", "CleanData")
DataOut <- file.path("..","Data", "CleanData")
PlotsOut <- file.path("..","Output", "Figures")
PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")

@@

# comment rows that are not included in grid arrange 
LayoutNiche <- rbind(
                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment for MIT9313
                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment for MIT9313
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(1, 1, 1, 1, 4),   # For 250 uM O2
                     c(1, 1, 1, 1, 4)    # For 250 uM O2
                     )

@@

p3_Red <- grid.arrange(
                       # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment for MIT9313
                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                         theme(legend.position = 'none'), 
                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                         theme(legend.position = 'none'), 
                        # legend1,   # remove comment for MIT9313
                        legend2, 
                        legend3, 
                       layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )

# for presentation
  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)

@@

p3_Blue <- grid.arrange(
                         # ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),  
                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),                          # legend1,    # remove comment for MIT9313
                        legend2, 
                        legend3, 
                        layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 10, width = 6)

# for presentation
  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 7.6, width = 6)

@@

```{r save plots}

 ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)

# MED4 GAM is Fig4.tiff
# SS120 GAM is Fig6.tiff
# MIT9313 GAM is Fig8.tiff
 ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10)
